Measuring E-Mail Header Injections on the World Wide Web

### 2016-09-18 Background/history.tex
updated for WWW paper

% TODO: Change all domains to example.com - DONE.
% TODO: Sai, this is the first time we mention SMTP, need more background and a reference to the RFC.

@@

>>>>

@@

%TODO Adam: added this para abt E-Mail Header Injection history from CVE
We gathered data from the Common Vulnerabilities and Exposures (CVE)~\cite{cve} database to get an idea of the distribution of \ehi vulnerabilities reported over time. We found 28 reports of \ehi from the CVE (shown in Table~\ref*{tab:history}).

From the table, it can be seen that even though a lot of \ehi vulnerabilities were found in the earlier years (2005-07), there have been several recently discovered \ehi vulnerabilities which suggests that it is still a very real threat and is relevant to modern web security.

\input{Background/history_table}

### 2016-09-18 Background/lang_aff.tex
fixed todos in evaluation
updated for WWW paper

\noindent{\textbf{Python}}
A bug was filed about an \ehi vulnerability in Python's implementation of the \texttt{email.header} library and the header parsing functions allowing newlines in early 2009, which was followed by a partial patch in early 2011.

Unfortunately, the bug fix was only for the \texttt{email.header} package, and thus exists in other frequently used packages such as \texttt{email.parser}, where both the classic \texttt{Parser()} and the newer \texttt{FeedParser()} contain \ehi vulnerabilities even in the latest versions: \texttt{2.7.11} and \texttt{3.5}. The bug fix was also not backported to older versions of Python.
There is no mention of the vulnerability in the Python documentation for either library.
A working code sample of the vulnerability, written in Python 2.7.11, is shown in Listing~\ref{code:pyemi}.

@@

\noindent{\textbf{Ruby}} 
From our preliminary testing Ruby's built-in \texttt{Net::SMTP} library also has an \ehi library. This is not documented on the library's homepage.
%A working code sample of the vulnerability, written in Ruby 2.0.0 (the latest stable version at the time of writing), is shown in Listing~\ref{code:rubyemi}.

%\input{Background/ruby.tex}

>>>>

\begin{sloppypar}
\noindent{\textbf{Python}}
A bug was filed about an \ehi vulnerability in Python's implementation of the \texttt{email.header} library and the header parsing functions allowing newlines in early 2009, which was followed by a partial patch in early 2011.
\end{sloppypar}

Unfortunately, the bug fix was only for the \texttt{email.header} package, and thus exists in other frequently used packages such as \texttt{email.parser}, where both the classic \texttt{Parser()} and the newer \texttt{FeedParser()} contain \ehi vulnerabilities even in the latest versions: \texttt{2.7.11} and \texttt{3.5}. The bug fix was also not backported to older versions of Python.
There is no mention of the vulnerability in the Python documentation for either library. Contrary to PHP's behavior of overwriting existing headers, Python only recognizes the first occurrence of a header, and ignores duplicate headers.
A working code sample of the vulnerability, written in Python 2.7.11, is shown in Listing~\ref{code:pyemi}.

@@

\begin{sloppypar}
\noindent{\textbf{Ruby}}
From our preliminary testing Ruby's built-in \texttt{Net::SMTP} library also has an \ehi vulnerability. This is not documented on the library's homepage.
%A working code sample of the vulnerability, written in Ruby 2.0.0 (the latest stable version at the time of writing), is shown in Listing~\ref{code:rubyemi}.
\end{sloppypar}
%\input{Background/ruby.tex}

### 2016-09-18 Discussion/limits.tex
fixed captchas
updated for WWW paper

\subsection[Limitations]{Limitations}
\label{limitations}

		Because our system is fully automated, it is also susceptible to being stopped by mechanisms in web applications that prevent automated crawls or form submissions. Measures such as CAPTCHA (Completely Automated Public Turing test to tell Computers and Humans Apart) and hidden form fields are often used to detect bots~\cite{captchas3, captchas2}.

		We made sure that we do not fuzz hidden fields in the form, however, despite considerable active research in breaking CAPTCHAs~\cite{captchas2, captchas}, breaking CAPTCHAs remains out of the scope of this project.

@@

		Thus, our system will not see dynamically injected forms and hence is unable to detect whether \ehi vulnerabilities are present in these forms. The workaround would be to use a JavaScript engine to query for the \texttt{document.getElementsByTagName('html')[0].innerHTML} (from inside web browser automation tools such as Selenium), then use that as the source HTML. We chose not to do this for performance reasons.

@@

        Because we search for the words \texttt{e-mail}, \texttt{mail}, or \texttt{email} within the HTML form, if the website does not use English names for its forms our system will not be able to find the presence of an \email field. An example is shown in Listing~\ref{code:htmlfrench}. Here, the French word for \texttt{e-mail}---courrier électronique---is used, and our system is unable to find the presence of the e-mail form.

@@

\begin{lstlisting}[language=HTML,caption={HTML page with e-mail form, written in a different language - French.},label={code:htmlfrench}, literate=%
	{é}{{\'e}}1, float]
<!doctype html>
<html lang="fr">
<head>
<meta charset="utf-8">
<meta name="author" content="XYZ">
<title>Mock Email</title></head>
<body>
<form action="{path-to-back-end}" method="post">
<input type="text" placeholder="courrier électronique"
	name="courrier_électronique"><br>
<textarea name="msg" rows="20" cols="120"></textarea>
<input type="submit" value="courrier électronique!">
</form></body>
</html>
\end{lstlisting}

>>>>

\subsection[Limitations]{Limitations}
\label{limitations}
		Because our system is fully automated, it is also susceptible to being stopped by mechanisms in web applications that prevent automated crawls or form submissions. Measures such as CAPTCHA, hidden form fields and CSRF (Cross-site Request Forgery~\cite{csrf}) tokens are often used to detect bots~\cite{captchas3, captchas2}.

		We made sure that we do not fuzz hidden fields in the form, and because our system does not depend on authenticated sessions, CSRF tokens do not pose an issue. However, despite considerable active research in breaking CAPTCHAs~\cite{captchas2, captchas}, breaking CAPTCHAs remains out of the scope of this project.

@@

		Thus, our system will not see dynamically injected forms and hence is unable to detect whether \ehi vulnerabilities are present in these forms. The workaround would be to use a JavaScript engine to query for the \texttt{document.getElementsByTagName('html')[0].innerHTML} (from inside web browser automation tools such as Selenium), then use that as the source HTML.

		%TODO Adam: added a table here, and explanation about performance tradeoffs with Selenium and bs4.
		A comparison of the running times between the different approaches is shown in Table~\ref{tab:perf}. Because using Selenium results in a slowdown of \slowSelenium, we chose not to do this for performance reasons.

		\begin{table}
			\centering
			\normalsize
			\begin{tabular}{|p{4cm}|c|c|}
				\hline
				\multicolumn{1}{|c}{\textbf{Method}} &
				\multicolumn{1}{|c|}{\textbf{Running time}} &
				\multicolumn{1}{|c|}{\textbf{Slowdown}}
				\\
				\hline
				\centering Using our pipeline & 629.043 & - \\
				\hline
				\centering Adding Selenium to our pipeline & 919.372 & \slowSelenium \\
				\hline				
				\centering Detecting \email fields by parsing each field instead of `grep'ing inside form & 707.154 & \slowParse \\								
				\hline
			\end{tabular}
			\caption[\titlecap{}]{Running times in seconds for crawling, parsing, and detecting presence of \email fields in 1000 random wikipedia pages.}
			\label{tab:perf}
		\end{table}

        Because we search for the words \texttt{e-mail}, \texttt{mail}, or \texttt{email} within the HTML form, if the website does not use English names for its forms our system will not be able to find the presence of an \email field. An example is shown in Listing~\ref{code:htmlfrench}. Here, the French word for \texttt{e-mail}---courrier électronique---is used, and our system is unable to find the presence of the e-mail field.

@@

@@

\begin{lstlisting}[language=HTML,caption={e-mail field in a different language - French.},label={code:htmlfrench}, literate=%
	{é}{{\'e}}1, float]
<input type="text" 
placeholder="courrier électronique"
name="courrier_électronique">
\end{lstlisting}

### 2016-09-18 Results/pipeline.tex
updated for WWW paper

In our fuzzing attempts, the same behavior is repeated. We fuzzed \fuzzed\ forms with the regular payload, which resulted in a total of \recd\ e-mails (\recdDelta). After analysis of the received e-mails, we further fuzzed \fuzzed\ forms, which resulted in \success\ e-mails (\successDelta) which contain the vulnerability across \ips IP Addresses corresponding to \domains domains.
\input{Results/pipeline_table}

>>>>

In our fuzzing attempts, the same behavior is repeated. We fuzzed \fuzzed\ forms with the regular payload, which resulted in a total of \recd\ e-mails (\recdDelta). After analysis of the received e-mails, we further fuzzed \malfuzzed\ forms, which resulted in \success\ e-mails (\successDelta) which contain the vulnerability across \ips IP Addresses corresponding to \domains domains.

%TODO Adam: added the reason for the reduction in the numbers, and accept that we do not have the data to quantify about captcha/csrf
We attribute the difference in the number of forms found to the number of forms fuzzed (a difference of \diffFoundFuzz forms) to the presence of bot-blocking mechanisms on a website (discussed in Section~\ref{limitations}), though we do not know what percentage was caused by the individual bot-blocking mechanisms discussed in Section~\ref{limitations}.

We would like to remark that over 1\% of the forms that were not fuzzed (100 out of \diffFoundFuzz) were also tested manually using PostMan to generate HTTP requests with payloads to verify that our system was working as intended.

\input{Results/pipeline_table}

### 2016-09-18 System/components.tex
fixed references and spacing
fixed captchas
updated for WWW paper

\subsubsection{Fuzzer}
\label{Comp:Fuzzer}
% Adam: we should call these something else but modules. We already have the top two modules, which are composed of components, now we need to split these into something (not components again). - DONE
The Fuzzer is the only component that interacts directly with the external web applications. The Fuzzer is split into smaller parts, each of which is responsible for a particular type of fuzzing.  The system injects payloads in two stages: the goal is to reduce the total number of HTTP requests the system generates to detect an \ehi vulnerability. Making HTTP requests is an expensive process~\cite{McGrath2009}, and can cause bottlenecks in a Crawler-Fuzzer system~\cite{ShkapenyukTorstenSuel2001}.
The two different types of payloads used for fuzzing are:
\paragraph{Non-Malicious Payload}
\label{Comp:Fuzzer:nmp}
The regular or non-malicious payload is simply an \email address. The goal is to see if the web application will send an \email message based on our input. The specific format of the \email is \texttt{reguser(xxxx)@example.com}, where \texttt{xxxx} is replaced by an internal id that uniquely maps the payload to the form, and \texttt{example.com} is replaced by our domain.

@@

\begin{table}[tbp]
	\centering
	\begin{tabular}{|c|c|c|}
		\hline
		\multicolumn{1}{|c|}{\textbf{Payload}} & \multicolumn{1}{c}{\textbf{Languages covered}} & \multicolumn{1}{|c|}{\textbf{Platforms covered}}\\
		\hline
		1 & PHP, Java, Ruby, etc. & Unix\\
		\hline
		2 & PHP, Java, Ruby, etc. & Windows\\
		\hline
		3 & Python & Unix\\
		\hline
		4 & Python & Windows\\
		\hline
	\end{tabular}
	\caption[\titlecap{Payload coverage}]{Payload coverage, each payload covers a different platform/language.}
	\label{tab:payloadcov}
\end{table}

@@

To find this, we parse each received \email, and check whether \emph{any} of the fields we injected with data appear as part of either the headers or the body of the \email. If they do, we add them to the list of fields that can potentially result in an \ehi vulnerability for the given \email. We then pass on this information back to the Fuzzer pipeline, along with the vulnerable form.

>>>>

\subsubsection{Fuzzer}
\label{Comp:Fuzzer}
% Adam: we should call these something else but modules. We already have the top two modules, which are composed of components, now we need to split these into something (not components again). - DONE
The Fuzzer is the only component that interacts directly with the external web applications. The Fuzzer is split into smaller parts, each of which is responsible for a particular type of fuzzing.  The system injects payloads in two stages: the goal is to reduce the total number of HTTP requests the system generates to detect an \ehi vulnerability. Making HTTP requests is an expensive process~\cite{httpperf}, and can cause bottlenecks in a Crawler-Fuzzer system~\cite{ShkapenyukTorstenSuel2001}.
The two different types of payloads used for fuzzing are:
\paragraph{Non-Malicious Payload}
\label{Comp:Fuzzer:nmp}
The regular or non-malicious payload is simply an \email address. The goal is to see if the web application will send an \email message based on our input. The specific format of the \email is \texttt{reguser(xxxx)@example.com}, where \texttt{xxxx} is replaced by an internal id that uniquely maps the payload to the form, and \texttt{example.com} is replaced by our domain.

@@

\begin{table}[tbp]
	\centering
	\normalsize
	\begin{tabular}{|c|c|c|}
		\hline
		\multicolumn{1}{|c|}{\textbf{Payload}} & \multicolumn{1}{c}{\textbf{Languages covered}} & \multicolumn{1}{|c|}{\textbf{Platforms covered}}\\
		\hline
		1 & PHP, Java, Ruby, etc. & Unix\\
		\hline
		2 & PHP, Java, Ruby, etc. & Windows\\
		\hline
		3 & Python & Unix\\
		\hline
		4 & Python & Windows\\
		\hline
	\end{tabular}
	\caption[\titlecap{Payload coverage}]{Payload coverage, each payload covers a different platform/language.}
	\label{tab:payloadcov}
\end{table}

@@

%TODO Adam: made clear that ALL input fields that appear in the email are fuzzed, with examples like name, username, etc.
To find this, we parse each received \email, and check whether \emph{any} of the fields we injected with data appear as part of either the headers or the body of the \email. These could be fields such as name, date of birth, username, etc. If they do, we add them to the list of fields that can \emph{potentially} result in an \ehi vulnerability for the given \email.

We then pass on this information back to the Fuzzer pipeline, along with the vulnerable form, where these fields are \emph{also} fuzzed along with the \email fields to check for the presence of \ehi.

### 2016-09-18 abstract.tex
updated for WWW paper

\begin{abstract}
	\ehi vulnerability is a class of vulnerability that can occur in web applications that use user input to construct \email messages. \ehi is possible when the mailing script fails to check for the presence of \email headers in user input (either form fields or URL parameters). The vulnerability exists in the reference implementation of the built-in mail functionality in popular languages such as PHP, Java, Python, and Ruby. With the proper injection string, this vulnerability can be exploited to inject additional headers, modify existing headers, and  alter the content of the \email.

	This paper presents a scalable mechanism to automatically detect \ehi vulnerabilities and uses this mechanism to quantify the prevalence of \ehi vulnerabilities on the web. Using a black-box testing approach, the system crawled \urls URLs to identify web pages which contained form fields. \forms such forms were found by the system, of which \emailforms forms contained \email fields. We then tested \fuzzed forms to see if they would send us an \email, and \recd forms sent us an \email. Of these, \malfuzzed forms were tested with \ehi payloads and, of these, we found \success vulnerable URLs across \domains domains. Then, to demonstrate that \ehi vulnerabilities are actively being exploited to create a spamming platform, we found \ipsblacklist IPs that were vulnerable on spamming blacklists. This work shows that \ehi vulnerabilities are widespread and deserve future research attention.
\end{abstract}

>>>>

\begin{abstract}
	\ehi vulnerability is a class of vulnerability that can occur in web applications that use user input to construct \email messages. \ehi is possible when the mailing script fails to check for the presence of \email headers in user input (either form fields or URL parameters). We discovered that the vulnerability exists in the reference implementation of the built-in \email functionality in the popular languages PHP, Java, Python, and Ruby. With the proper injection string, this vulnerability can be exploited to allow an attacker to inject additional headers, modify existing headers, and alter the content of the \email.

	While \ehi vulnerabilities are known by the community, and some commercial vulnerability scanners claim to discover \ehi vulnerabilities, they have never been studied by the academic community. This paper presents a scalable mechanism to automatically detect \ehi vulnerabilities and uses this mechanism to quantify the prevalence of \ehi vulnerabilities on the web. Using a black-box testing approach, the system crawled \urls URLs to identify web pages which contained form fields. \forms such forms were found by the system, of which \emailforms forms contained \email fields. We then fuzzed \fuzzed forms to see if they would send us an \email, and \recd forms sent us an \email. Of these, \malfuzzed forms were tested with \ehi payloads and, of these, we found \success vulnerable URLs across \domains domains. Then, to measure if \ehi vulnerabilities are actively being exploited to create a spamming platform, we found evidence that \ipsblacklist IPs that were vulnerable to \ehi are on spamming blacklists. This work shows that \ehi vulnerabilities are widespread and deserve future research attention.
\end{abstract}

### 2016-09-18 introduction.tex
fixed some small things Fixed all todos till sys design
updated for WWW paper

\section{Introduction}
The World Wide Web has single-handedly brought about a change in the way we use computers. The ubiquitous nature of the web has made it possible for anyone to access information and services anywhere and on multiple devices such as phones, laptops, personal digital assistants, TVs, and cars. This access has ushered in an era of web applications which depend on user input. While this rapid pace of development has improved the speed of dissemination of information, it does come at a cost. As users move more and more of their personal and financial information to web applications, attackers are responding by using web application vulnerabilities to access this lucrative data.

%% Adam: I don't see how this adds to our story
%% Attackers have an added incentive to break into user's e-mail accounts more than ever. E-Mail accounts are usually connected to almost all other online accounts of a user, and e-mails continue to serve as the principal mode of official communication on the web for most institutions. Thus, the impact an attacker can have by having control over the \email communication sent by websites to users is of an enormous magnitude.

% TODO: Sai, can you add a reference to command injection vulnerabilities here? DONE.
Many common and well-known web application vulnerabilities, such as SQL Injection and Cross-Site Scripting~\cite{OWASPT10}, are command injection vulnerabilities~\cite{commandinjection}, where malicious user input is used to alter the structure of a command (a SQL query in the case of SQL Injection and JavaScript code in the case of Cross-Site Scripting). Developers of web applications must have proper sanitization routines in place to use user input as part of these commands.

\ehi vulnerabilities are a lesser-known command injection vulnerability. \ehi can be considered as the \email equivalent of HTTP Header Injection~\cite{wiki:HTTP_headerinjection}. This vulnerability exists in the implementation of the built-in \texttt{mail} functionality in popular languages such as PHP, Java, Python, and Ruby. The format of \email messages is defined by the Simple Mail Transfer Protocol (SMTP)~\cite{rfc5322}. Each \email message is represented by a series of headers separated by newlines, followed by the body content (separated from the headers by two newlines). Some of these headers are mandatory (From, To, Date), but the headers could also include other information like the Subject, CC, BCC, etc.

\textbf{Sai: I believe that the discussion of SMTP Headers belongs here, before we say that E-Mail Header Injection can manipulate the headers. Do I need to include the message format as a listing? I think its superfluous, but let me know.}

@@

%% The objective of our research is to study the prevalence of this vulnerability on the World Wide Web, and identify whether further research is required in this area.

While some command injection vulnerabilities have received extensive attention from the research community, \ehi vulnerabilities have received little focus. Therefore, we study the prevalence of \ehi vulnerabilities on the web. We performed a crawl of the web, extracted forms with \email fields, and injected them with different payloads to infer the existence of an \ehi vulnerability. We then audited received \emails to see if any of the injected data was present. This allowed us to classify whether a particular URL was vulnerable to the attack. Our automated system works in a black-box manner, without looking at the web application's source code, and only analyzes the \emails we receive based on the injected payloads.
\\

\noindent{}In summary, we make the following contributions:

\begin{itemize}

@@

\item We develop a system to crawl the web and automatically detect \ehi vulnerabilities.

>>>>

\section{Introduction}
The World Wide Web has single-handedly brought about a change in the way we use computers. The ubiquitous nature of the web has made it possible for anyone to access information and services anywhere and on multiple devices such as phones, laptops, personal digital assistants, TVs, and cars. This access has ushered in an era of web applications which depend on user input. 
While the rapid pace of development has improved the speed of information dissemination, it comes at a cost. As users move more and more of their personal and financial information to web applications, attackers are responding by using web application vulnerabilities to access this lucrative data.

Many common and well-known web application vulnerabilities, such as SQL Injection and Cross-Site Scripting~\cite{OWASPT10}, are command injection vulnerabilities~\cite{commandinjection}, where malicious user input is used to alter the structure of a command (a SQL query in the case of SQL Injection and JavaScript code in the case of Cross-Site Scripting). Developers of web applications must use the correct sanitization routine in all paths leading from user input to a command.

\ehi vulnerabilities are a lesser-known command injection vulnerability\footnote{\ehi can be considered as the \email equivalent of HTTP Header Injection~\cite{wiki:HTTP_headerinjection}}. We verified that this vulnerability exists in the implementation of the built-in \email functionality in the popular languages PHP, Java, Python, and Ruby. The format of \email messages is defined by the Simple Mail Transfer Protocol (SMTP)~\cite{rfc5322}. Each \email message is represented by a series of headers separated by newlines, followed by the body content (separated from the headers by two newlines). Some of these headers are mandatory (From, To, Date), but the headers could also include other information such as the Subject, CC, BCC, etc.

@@

While some command injection vulnerabilities have received extensive attention from the research community, \ehi vulnerabilities have received little focus. In fact, the Acunetix vulnerability scanner contains an AcuMonitor component which claims to detect \ehi vulnerabilities while scanning~\cite{acumonitor}. Unfortunately, as a commercial product, little is known about how AcuMonitor detects \ehi vulnerabilities.

To shed light on this little-studied vulnerability class, we describe \ehi vulnerabilities and measure \ehi vulnerabilities on the web. To perform this measurement, we crawled the web, extracted forms with \email fields, and injected them with different payloads to infer the existence of an \ehi vulnerability. We then audited received \emails to see if any of the injected data was present. This allowed us to classify whether a particular URL was vulnerable to the attack. Our automated system works in a black-box manner, without looking at the web application's source code, and only analyzes the \emails we receive based on the injected payloads.
%TODO Adam: Added a line to make clear that we wanted a quantification before attempting something like a source-code analyzer. This addresses reviewer 690B's concerns.

The objective of our research is to study the prevalence of this vulnerability on the World Wide Web and identify whether further research is required in this area.
\\

\noindent{}In summary, we make the following contributions:
\begin{itemize}

@@

\item We develop an open-source system to crawl the web and automatically detect \ehi vulnerabilities.
